Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making

### 2021-09-28 proposal.tex
Merge network subsection of ABM paper.
Add intro and part of experiment ch.
Change terminology in ch2 from 'efficiency' to 'productivity'.
Figures and title page.

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{apacite}
\usepackage{bbding}
\usepackage{courier}
\usepackage{epigraph}
\usepackage{graphicx}
\usepackage{helvet}
\usepackage[utf8]{inputenc}
\usepackage[switch]{lineno}
\usepackage[normal]{threeparttable}
\usepackage{titlesec}
\usepackage{url}

@@

@@

\linenumbers

@@

\maketitle

\begin{abstract}
\include{abstract.tex}
\end{abstract}

@@

\chapter{Introduction}
\include{ch-intro.tex}

\chapter{Network structure, productivity, and performance in WikiProjects}
\include{ch-wp-prod-perf.tex}

\chapter{Small interlocking groups improve mass deliberation in the presence
of strong social influence}
\include{ch-abm.tex}

\chapter{Experimental evaluation of Network Deliberaiton}

\chapter*{Acknowledgements}
%\include{acknoledgements.tex}

>>>>

\usepackage[ruled,vlined]{algorithm2e}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{apacite}
\usepackage[toc,page]{appendix}
\usepackage{bbding}
\usepackage{courier}
\usepackage{epigraph}
\usepackage{graphicx}
\usepackage{helvet}
\usepackage[utf8]{inputenc}
\usepackage[switch]{lineno}
\usepackage[normal]{threeparttable}
\usepackage{titlesec}
\usepackage{url}

@@

\renewcommand{\labelenumii}{\theenumii}
\renewcommand{\theenumii}{\theenumi.\arabic{enumii}.}

@@

%\linenumbers

@@

\begin{titlepage}
   \begin{center}
       \vspace*{1cm}

       \textbf{\Large Network Deliberation: The role of network structure in large-scale, internet-enabled, participatory decision-making}

       \vspace{1.5cm}

       \textbf{Edward L. Platt}

       \today

       \vfill

       Dissertation Proposal\\
       Doctor of Philosophy \\
       University of Michigan \\
       School of Information

       \vspace{0.8cm}

   \end{center}
    {\bfseries Doctoral Committee:}\\
    Associate Professor Daniel M. Romero \\
    Professor Scott E. Page \\
    Associate Professor Tawanna Dillahunt \\
    Assistant Professor Ceren Budak

\end{titlepage}

%\begin{abstract}
%\include{abstract.tex}
%\end{abstract}

@@

\listoffigures
\listoftables

\chapter{Introduction}
\label{chap:intro}
%\include{ch-intro.tex}

\chapter{Network structure, productivity, and performance in WikiProjects}
\label{chap:wp-prod-perf}
%\include{ch-wp-prod-perf.tex}

\chapter{Small interlocking groups improve mass deliberation in the presence
of strong social influence}
\label{chap:abm}
%\include{ch-abm.tex}

\chapter{Experimental evaluation of Network Deliberaiton}
\label{chap:experiment}
\include{ch-experiment.tex}

%\chapter*{Acknowledgements}
%\include{acknoledgements.tex}

\begin{appendices}

\chapter{The NK-Model}
\label{apx:nk}
\include{apx-nk.tex}

\chapter{Interview Script}
\label{apx:interview}
\include{apx-interview.tex}

\end{appendices}
